Informative Oceanographic Sampling using Excursion Probabilities for Multivariate Random Fields

### 2019-05-27 main_new.tex
updates

% == Trygve Test
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}

@@

In our setting we study two variables; temperature and salinity, which
together characterize the phenomenon taking place in the river plume. At
location $\bx \in \mathcal{M} \subset \mathbf{R^2}$, we define the two
process variables by
$\bxi(\bx)=(\xi_a(\bx),\xi_b(\bx))$. %In practice there is of course time variability, but we assume this to be negligible during the AUV operation. Depth variability could also be important in some cases, but in the current application the with depths only a few meters this is considered irrelevant for mapping the phenomenon.

In the context illustrated by Figure \ref{fig:river4}, interest is on spatial separation of cold freshwater. 
Because a main goal is classifying the water masses, ES variability is a useful sampling criterion for guiding the observation effort of the AUV. 
A bivariate ES is here defined via joint variables being below thresholds, at individual locations, for the process over the spatial domain $\mathcal{M}$.
Denoting the threshold for temperature by $T_a$ and the threshold for salinity by $T_b$,
we use the following definition;
 \begin{equation}\label{ES}
     \mbox{ES} = \{\bx \in \mathcal{M} | \xi_a(\bx) < T_a,\xi_b(\bx) < T_b\}.
 \end{equation}
The excursions could also be defined as larger than threshold, or within a boundary of limits for the two variables. Calculations and interpretations will be similar in these different cases.

>>>>

% == Trygve Test
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
\newcommand{\kcomment}[1]{{\color{blue}{\{KR: #1\}}}}

@@

In our setting we study two variables; temperature and salinity, which
together characterize the phenomenon taking place in the river plume as
they define the gradients which define the frontal zone we wish to
observe. At location $\bx \in \mathcal{M} \subset \mathbf{R^2}$, we
define the two process variables by
$\bxi(\bx)=(\xi_a(\bx),\xi_b(\bx))$. %In practice there is of course time variability, but we assume this to be negligible during the AUV operation. Depth variability could also be important in some cases, but in the current application the with depths only a few meters this is considered irrelevant for mapping the phenomenon.

% In the context illustrated by Figure \ref{fig:river4},
Our focus is on spatial separation of cold freshwater from the saline
waters of the fjord and to be able to classify these water masses. In
this context, ES variability is a useful sampling criterion for guiding
the observation effort of the AUV. A bivariate ES is defined via joint
variables being below thresholds, at individual locations, for the
process over the spatial domain $\mathcal{M}$. Denoting the threshold
for temperature by $T_a$ and the threshold for salinity by $T_b$, we use
the following definition;
 \begin{equation}\label{ES}
     \mbox{ES} = \{\bx \in \mathcal{M} | \xi_a(\bx) < T_a,\xi_b(\bx) < T_b\}.
 \end{equation}
The excursions could also be defined as larger than threshold, or within a boundary of limits for the two variables. Calculations and interpretations will be similar in these different cases.
